---
title: "Untitled"
output: html_document
---

# This is a header #
## Header 2 ##
### Header 3 ###

This is __bold text__
* Item a
* Item b

1. Item 1
2. Item 2
4. Item 3


> This is a block quote

~~strikethrough~~

This an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and Microsoft Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **R Tools | Publish | Preview** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r}
summary(cars)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{r, echo=FALSE}
linm <- lm(faithful$eruptions ~ faithful$waiting)
plot(faithful$waiting, faithful$eruptions)
abline(linm)
```